Experiment 2

### 2018-03-20 experiment_2/experiment_2.tex
update

Comments: The story I seem to get from this is (roughly) that the worse the algorithm that the incumbent plays is, the better the entrant will do. Thus, the incumbent should want to play a better algorithm. However, in order for the entrant to do as well as possible, the entrant should in fact play a worse algorithm! If you think of it from the incumbent point of view, the incumbent is in the market first and so wants to learn as much as possible before the entrant comes in (thus does better with a better algorithm since it should have learned more by the time the entrant enters).  From the entrant point of view, since the incumbent has already learned something in order to have any chance to compete you do better by purely exploiting than by engaging in potentially suboptimal exploration. Two follow-up questions: Will this result hold if we run the simulations for more periods? What will happen to this result if we increase memory size?

>>>>

Comments: The story I seem to get from this is (roughly) that the worse the algorithm that the incumbent plays is, the better the entrant will do. Thus, the incumbent should want to play a better algorithm. However, in order for the entrant to do as well as possible, the entrant should in fact play a worse algorithm! If you think of it from the incumbent point of view, the incumbent is in the market first and so wants to learn as much as possible before the entrant comes in (thus does better with a better algorithm since it should have learned more by the time the entrant enters).  From the entrant point of view, since the incumbent has already learned something in order to have any chance to compete you do better by purely exploiting than by engaging in potentially suboptimal exploration. Two follow-up questions: Will this result hold if we run the simulations for more periods? What will happen to this result if we increase memory size? Another question is whether or not the effect is driven by the better information the incumbent has or the effect of reputation.
\vspace{0.5cm}

This motivates the following experiment which has an identical setup as before (principal 2 gets to be in the game for 200 periods before principal 1), however after the 200 rounds we are going to erase the memory of the agents. Thus, when principal 1 enters the market the incumbent (principal 2) does not have an advantage in terms of reputation, but only in terms of the information s/he possesses. The results don't change much qualitatively from the case we first considered.
\includepdf[pages={-}]{no_reputation_tournament_table}

Another check of the robustness of the results: The memory size is increased to 250 so that when principal 1 enters the market the entire history of the incumbent is contained in the information set of the incumbent.
\includepdf[pages={-}]{more_memory_tournament_table}
